manuscript_figures

### 2024-06-28 scripts/manuscript_figures.Rmd
updated nmds script

#make community matrix - extract columns with abundance information
com = invert.count[,6:ncol(invert.count)]

# Calculate Bray-Curtis dissimilarity
m_com <- vegdist(com, method = "bray")

# Check for warnings and errors
if (any(warnings())) {
  warning("Warnings during distance calculation:", warnings())
}

# Remove empty rows (if applicable)
m_com <- as.matrix(m_com[complete.cases(m_com), ])

# Check dimensions of m_com after removing empty rows
dim(m_com)

# Perform nMDS with Bray-Curtis dissimilarity
nmds <- metaMDS(m_com, distance = "bray")

>>>>

# Convert data from long to wide for nmds
wide_data <- invert.count %>%
  dplyr::select(TRANSECT, YEAR, SITE, type, abundance) %>%
  pivot_wider(names_from = type, values_from = abundance, values_fill = list(abundance = 0))

# Ensure abundance columns are numeric
wide_data <- wide_data %>%
  mutate(across(crustacean:molluscs, as.numeric))

# Calculate Bray-Curtis dissimilarity
m_com <- vegdist(wide_data[, -c(4:6)], method = "bray")

# Perform nMDS
nmds <- metaMDS(m_com, distance = "bray")
